Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-03-05 paper/paper.tex
minor change

\subsubsection{Optimization}

@@

%%\begin{table}[h!]
%%  \small
%%  \caption{\label{table:weight}Weight Combinations.}
%%  \centering
%%  \begin{tabular}{lrrp{15cm}}
%%    \toprule
%%    \multicolumn{1}{c}{Name} &
%%    \multicolumn{1}{c}{Weights} &
%%    \multicolumn{1}{c}{Rank} \\
%%    \midrule
%%    Ping Scan & - & - \\
%%    SYN Flood & - & - \\
%%    JBoss JMX & 1,0,1,1 & 107 \\
%%    WeBid & - & - \\    
%%    ColdFusion & 0,1,1,1 & 7 \\
%%    .htaccess access & 0,1,1,1 & 11 \\
%%    .idq access & 0,1,1,1 & 7 \\
%%    iisadmin access & 0,1,1,1 & 2 \\
%%    /system32/ in URI & 0,1,1,1 & 11 \\
%%    Script tag in URI & 0,1,1,1 & 9 \\
%%    \bottomrule
%%  \end{tabular}
%%\end{table}
%%

@@

This section evaluates the importance of each proposed heuristic
function. More precisely, we evaluated the use of \tname{} without
each of those functions with the goal of checking whether or not each
of them contributes to the overall performance of the technique. We
conducted that experiment by assigning the weight of the corresponding
function to zero---effectively, disabling the function---and comparing
the result with \tname\ using default weights, obtained with the
procedure described on Section~\Fix{xxx}.

Table~\ref{table:weights} shows results. Column ``Name'' shows the
name of the attack and column ``All'' shows the result of \tname\ with
all heuristic functions enabled (same as column ``Rank (step 3)'' from
Table~\Fix{xxx}). The remaining columns show results supressing one
heuristic function. An up arrow indicates that, considering that
particular data point, the performance of \tname{} on that
configuration is worse when compared to \tname's default
configuration. A down arrow, appearing highlighted in the table,
indicates the contrary.

>>>>

\subsubsection{Optimization}
\label{sec:weight-optimization}

@@

%%\begin{table}[h!]
%%  \small
%%  \caption{\label{table:weight}Weight Combinations.}
%%  \centering
%%  \begin{tabular}{lrrp{15cm}}
%%    \toprule
%%    \multicolumn{1}{c}{Name} &
%%    \multicolumn{1}{c}{Weights} &
%%    \multicolumn{1}{c}{Rank} \\
%%    \midrule
%%    Ping Scan & - & - \\
%%    SYN Flood & - & - \\
%%    JBoss JMX & 1,0,1,1 & 107 \\
%%    WetedhhtedBid & - & - \\    
%%    ColdFusion & 0,1,1,1 & 7 \\
%%    .htaccess access & 0,1,1,1 & 11 \\
%%    .idq access & 0,1,1,1 & 7 \\
%%    iisadmin access & 0,1,1,1 & 2 \\
%%    /system32/ in URI & 0,1,1,1 & 11 \\
%%    Script tag in URI & 0,1,1,1 & 9 \\
%%    \bottomrule
%%  \end{tabular}
%%\end{table}
%%

@@

This section evaluates the importance of each proposed heuristic
function. To that end, we evaluated the use of \tname{} without each
of these functions with the goal of checking how much each of them
contributes to the overall performance of the technique. Recall that
the score a function $r$ is given by the weigthed average of the
values given by each heuristic function, \ie{} the score of $r$ is
obtained with the aggregate function $f(r)=\sum_{i}^{N}
w_i*f_i(r)/N;$, where $w_i$ is the weight of heuristic $i$, $f_i(r)$
is the score of heuristic $i$ on $r$, and $N$ is the number of
heuristic---four, in our case. To assess the value of each heuristic
function, we assigned its weight to zero---effectively, disabling the
function---and compared the result with \tname\ using default weights,
obtained with the procedure described on
Section~\ref{sec:weight-optimization}.

Table~\ref{table:weights} shows results. Column ``Name'' shows the
name of the attack and column ``All'' shows the result of \tname\ with
all heuristic functions enabled; as in column ``Rank (step 3)'' from
Table~\ref{table:results}. The remaining columns show results obtained
by running the same experiment as in Section~\ref{sec:answer-rqone},
but supressing one heuristic function. An up arrow indicates that,
considering that particular data point, the performance of \tname{} on
that configuration is worse when compared to \tname's default
configuration. A down arrow, appearing highlighted in the table,
indicates the contrary.

\Mar{--------------------------------- estou aqui}
